A Makefile for Developing Containerized \LaTeX\ Technical Documents

### 2020-12-23 ms.tex
fix ms.tex

The Makefile consists of the following minimal user interface:
\begin{lstlisting}[language=bash, style=lststyle, caption={Template make options.}]
make             # Generate the draft (fast) version.
make VER=--full  # Generate the full (slow) version.
make clean       # Remove the tmp/ directory.
\end{lstlisting}

@@

The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{tmp/} respectively.
An example of a \textit{results code} that generates the draft version \textit{document} in the field of neural networks would be a conditional that sets the number of epochs and training/validation/test samples to a low value.

@@

Additionally an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
\begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]
# Generate the first draft document version.
make
# Backup the first resulting pdf.
cp tmp/ms.pdf tmp/ms-previous.pdf
# Update the modification timestamp of main.py.
touch main.py
# Generate the second draft document version.
make
# Compare draft document versions byte by byte.
cmp tmp/ms.pdf tmp/ms-previous.pdf
# Compare draft document versions
# in a human readable form.
diffoscope tmp/ms.pdf tmp/ms-previous.pdf
\end{lstlisting}

>>>>

The Makefile can be called with the following options:
\begin{lstlisting}[language=bash, style=lststyle, caption={Makefile options.}]
make             # Generate the draft (fast) version.
make VER=--full  # Generate the full (slow) version.
make clean       # Remove the tmp/ directory.
\end{lstlisting}

@@

The only requirements that the Makefile imposes on \textit{code} is the presence of \textit{results code} that generates the draft and full versions of the \textit{document} and the presence of \textit{results code} and \textit{\LaTeX\ code} for saving/loading the \textit{results} to/from \textit{tmp/} respectively.
An example of a \textit{results code} that generates the draft version \textit{document} in the field of neural networks would be a conditional that sets the number of epochs and training/validation/test samples to a low value.

@@

Additionally, an \textit{author} can use the POSIX utility \textit{cmp} to compare \textit{documents} (generated in a different session, operating system or underlying hardware) byte by byte, and diffoscope\footnote{\url{https://diffoscope.org/}} for identifying sources of non-determinism as follows:
\begin{lstlisting}[language=bash, style=lststyle, caption={Test draft document version reproducibility. This can also be used as a test script when pushing or pull requesting to a remote repository.}]
# Generate the first draft document version.
make
# Backup the first resulting pdf.
cp tmp/ms.pdf tmp/ms-previous.pdf
# Update the modification timestamp of main.py.
touch main.py
# Generate the second draft document version.
make
# Compare draft document versions byte by byte.
cmp tmp/ms.pdf tmp/ms-previous.pdf
# Compare draft document versions
# in a human readable form.
diffoscope tmp/ms.pdf tmp/ms-previous.pdf
\end{lstlisting}
